---
title: "mhr: An R package to work with MakeHuman files"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Installation
```{r}
install.packages('devtools')
devtools::install_github('d-bohn/mhr')
```

## Rationale
[MakeHuman](http://www.makehumancommunity.org/) is a wonderful, free, open source, and user-friendly 3D model generator for human-like avatars. It is often used in conjuction with other 3D rendering and manipulation software for a complete end-to-end 3D modelling solution. However, despite MakeHuman's user-friendly approach, there is no command line interface, nor internal scripting. From a programatic standpoint, this make it particularly hard, for example, to batch process and manipulate files. Theoretically this can be done by adding a "plugin" written in python to the user's installation of MakeHuman, but this has a number of drawbacks.

This package provides some simple functions to work with MakeHuman files. In particular, it helps with batch processing of models.

## Getting started
Funcutions are provided (currently) to:

1) Read in a \code{.mhm} file
```{r}
mhm_file <- system.file('random_female.mhm', package = 'mhr')

mhm <- read_mhm(mhm_file)
```

This reads in a \code{.mhm} file to memory, and creates an object of class \code{mhm}.
MakeHuman model files are simple text files, so each file is parsed and saved to a list
object to be futher manipulated.

2) Randomize the 247 modifiers
```{r}
mhm_rand <- mhm_rand_modifiers(mhm,
                           sym = TRUE,
                           mod_limits = c(-0.6,1),
                           gender_limits = c(0,1),
                           breasts_limits = c('rand'),
                           age_limits = c(.363,1))
```

3) Write out a \code{.mhm} file
```{r}
write_mhm(mhm_rand, 'makehuman_random.mhm')
```

## Planned Features

- Manipulating camera angle in a user-friendly manner

- More detailed controller over how the modifiers are randomized

- Manipulating modifiers individually by name

- Converting \code{.mhm} files to \code{.obj} files

- Manipulating \code{.obj} files in a similar manner to \code{.mhm} files
